Estimating the magnetization distribution within rectangular rock samples

### 2016-07-25 manuscript/manuscript.tex

We have applied our method to invert the synthetic data produced
by a simulated rock sample (not shown) with $L_{x} = 16$~mm and 
$L_{y} = L_{z} = 3$~mm, according to the Figure \ref{fig:sample}.
This synthetic sample is formed by $P = 16$ juxtaposed prisms along 
the $x$-axis, where each prism has a uniform and high magnetization
(red dots in Figures \ref{fig:estimate-validation},
\ref{fig:estimate-pre-processing} and \ref{fig:estimate-sensor2sample}).
In all tests presented in this section, 
the simulated magnetic sensor has an square active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}). The
magnetic data produced by the synthetic sample on 
each plane $\alpha = 0, 1, 2, 3$ were calculated at
$N = 4,284$ points, on a set of $42$ regularly spaced lines 
that are parallel to the $x$-axis, each one with $102$ regularly
spaced points. The data were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $30,000$~$\mu$T. These data simulate
an observed data set.
Besides, we have simulated the misalignment problems 
described in the subsection \ref{subsec:Pre-processing}.
Table \ref{tab:misalignment-parameters} shows the parameters
$\theta$, $\Delta x^{\prime}$ and $\Delta y^{\prime}$ (Figure 
\ref{fig:acquisition_errors}b) representing these misalignments
in the magnetic data produced by the synthetic sample on
the planes $\alpha = 0, 1, 2, 3$.

@@

%\bibliography{bib-file}
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

\begin{thebibliography}{56}
\providecommand{\natexlab}[1]{#1}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{\textit{Aster et~al.}(2005)\textit{Aster, Borchers, and
  Thurber}}]{aster2005}
Aster, R.~C., B.~Borchers, and C.~H. Thurber (2005), \textit{Parameter
  Estimation and Inverse Problems, Volume 90 (International Geophysics)},
  Academic Press.

\bibitem[{\textit{Baratchart et~al.}(2013)\textit{Baratchart, Hardin, Lima,
  Saff, and Weiss}}]{baratchart2013}
Baratchart, L., D.~P. Hardin, E.~A. Lima, E.~B. Saff, and B.~P. Weiss (2013),
  Characterizing kernels of operators related to thin-plate magnetizations via
  generalizations of hodge decompositions, \textit{Inverse Problems},
  \textit{29}(1), 015,004, \doi{10.1088/0266-5611/29/1/015004}.

\bibitem[{\textit{Barnes}(2014)}]{barnes2014}
Barnes, G. (2014), Reconstructing the gravity gradient anomaly field from
  surveys with wide line spacing using equivalent source processing: an error
  analysis, \textit{Geophysical Prospecting}, \textit{62}(3), 646--657,
  \doi{10.1111/1365-2478.12098}.

\bibitem[{\textit{Barnes and Lumley}(2011)}]{barnes-lumley2011}
Barnes, G., and J.~Lumley (2011), Processing gravity gradient data,
  \textit{GEOPHYSICS}, \textit{76}(2), I33--I47, \doi{10.1190/1.3548548}.

\bibitem[{\textit{Baudenbacher et~al.}(2003)\textit{Baudenbacher, Fong, Holzer,
  and Radparvar}}]{baudenbacher2003}
Baudenbacher, F., L.~E. Fong, J.~R. Holzer, and M.~Radparvar (2003), Monolithic
  low-transition-temperature superconducting magnetometers for high resolution
  imaging magnetic fields of room temperature samples, \textit{Appl. Phys.
  Lett.}, \textit{82}(20), 3487--3489,
  \doi{http://dx.doi.org/10.1063/1.1572968}.

\bibitem[{\textit{Blackett}(1952)}]{blackett1952}
Blackett, P. M.~S. (1952), A negative experiment relating to magnetism and the
  earth{\textquoteright}s rotation, \textit{Philosophical Transactions of the
  Royal Society of London A: Mathematical, Physical and Engineering Sciences},
  \textit{245}(897), 309--370, \doi{10.1098/rsta.1952.0024}.

\bibitem[{\textit{Cordell}(1992)}]{cordell1992}
Cordell, L. (1992), A scattered equivalent-source method for interpolation and
  gridding of potential‐field data in three dimensions, \textit{GEOPHYSICS},
  \textit{57}(4), 629--636, \doi{10.1190/1.1443275}.

\bibitem[{\textit{Dampney}(1969)}]{dampney1969}
Dampney, C. N.~G. (1969), The equivalent source technique, \textit{GEOPHYSICS},
  \textit{34}(1), 39--53, \doi{10.1190/1.1439996}.

\bibitem[{\textit{Dodson et~al.}(1974)\textit{Dodson, Fuller, and
  Pilant}}]{dodson1974}
Dodson, R., M.~Fuller, and W.~Pilant (1974), On the measurement of the remanent
  magnetism of long cores, \textit{Geophysical Research Letters},
  \textit{1}(4), 185--188, \doi{10.1029/GL001i004p00185}.

\bibitem[{\textit{Egli and Heller}(2000)}]{egli2000}
Egli, R., and F.~Heller (2000), High-resolution imaging using a high-tc
  superconducting quantum interference device (squid) magnetometer, \textit{J.
  Geophys. Res.: Solid Earth}, \textit{105}(B11), 25,709--25,727,
  \doi{10.1029/2000JB900192}.

\bibitem[{\textit{Emilia}(1973)}]{emilia1973}
Emilia, D.~A. (1973), Equivalent sources used as an analytic base for
  processing total magnetic field profiles, \textit{GEOPHYSICS},
  \textit{38}(2), 339--348, \doi{10.1190/1.1440344}.

\bibitem[{\textit{Engl et~al.}(1996)\textit{Engl, Hanke, and
  Neubauer}}]{engl1996}
Engl, H.~W., M.~Hanke, and A.~Neubauer (1996), \textit{Regularization of
  Inverse Problems (Mathematics and Its Applications)}, Springer.

\bibitem[{\textit{Fong et~al.}(2005)\textit{Fong, Holzer, McBride, Lima,
  Baudenbacher, and Radparvar}}]{fong2005}
Fong, L.~E., J.~R. Holzer, K.~K. McBride, E.~A. Lima, F.~Baudenbacher, and
  M.~Radparvar (2005), High-resolution room-temperature sample scanning
  superconducting quantum interference device microscope configurable for
  geological and biomagnetic applications, \textit{Rev. Sci. Instrum.},
  \textit{76}(5), \doi{10.1063/1.1884025}.

\bibitem[{\textit{Fu et~al.}(2014)\textit{Fu, Lima, and Weiss}}]{fu2014}
Fu, R., E.~Lima, and B.~Weiss (2014), No nebular magnetization in the allende
  \{CV\} carbonaceous chondrite, \textit{Earth Planet. Sci. Lett.},
  \textit{404}, 54--66, \doi{10.1016/j.epsl.2014.07.014}.

\bibitem[{\textit{Gattacceca et~al.}(2006)\textit{Gattacceca, Boustie, Weiss,
  Rochette, Lima, Fong, and Baudenbacher}}]{gattacceca2006}
Gattacceca, J., M.~Boustie, B.~P. Weiss, P.~Rochette, E.~A. Lima, L.~E. Fong,
  and F.~J. Baudenbacher (2006), Investigating impact demagnetization through
  laser impacts and squid microscopy, \textit{Geology}, \textit{34}(5),
  333--336, \doi{10.1130/G21898.1}.

\bibitem[{\textit{Goree and Fuller}(1976)}]{goree-fuller1976}
Goree, W.~S., and M.~Fuller (1976), Magnetometers using rf-driven squids and
  their applications in rock magnetism and paleomagnetism, \textit{Reviews of
  Geophysics}, \textit{14}(4), 591--608, \doi{10.1029/RG014i004p00591}.

\bibitem[{\textit{Gusp\'{i} and Novara}(2009)}]{guspi-novara2009}
Gusp\'{i}, F., and I.~Novara (2009), Reduction to the pole and transformations
  of scattered magnetic data using newtonian equivalent sources,
  \textit{GEOPHYSICS}, \textit{74}(5), L67--L73, \doi{10.1190/1.3170690}.

\bibitem[{\textit{Hankard et~al.}(2009)\textit{Hankard, Gattacceca, Fermon,
  Pannetier-Lecoeur, Langlais, Quesnel, Rochette, and McEnroe}}]{hankard2009}
Hankard, F., J.~Gattacceca, C.~Fermon, M.~Pannetier-Lecoeur, B.~Langlais,
  Y.~Quesnel, P.~Rochette, and S.~A. McEnroe (2009), Magnetic field microscopy
  of rock samples using a giant magnetoresistance–based scanning
  magnetometer, \textit{Geochem., Geophys., Geosyst.}, \textit{10}(10),
  \doi{10.1029/2009GC002750}.

\bibitem[{\textit{Hansen and Miyazaki}(1984)}]{hansen-miyazaki1984}
Hansen, R.~O., and Y.~Miyazaki (1984), Continuation of potential fields between
  arbitrary surfaces, \textit{GEOPHYSICS}, \textit{49}(6), 787--795,
  \doi{10.1190/1.1441707}.

\bibitem[{\textit{Hunter}(2007)}]{hunter2007}
Hunter, J.~D. (2007), Matplotlib: A 2d graphics environment, \textit{Computing
  in Science \& Engineering}, \textit{9}(3), 90--95,
  \doi{10.1109/MCSE.2007.55}.

\bibitem[{\textit{Jackson et~al.}(2010)\textit{Jackson, Bowles, Lascu, and
  Solheid}}]{jackson2010}
Jackson, M., J.~A. Bowles, I.~Lascu, and P.~Solheid (2010), Deconvolution of u
  channel magnetometer data: Experimental study of accuracy, resolution, and
  stability of different inversion methods, \textit{Geochemistry, Geophysics,
  Geosystems}, \textit{11}(7), \doi{10.1029/2009GC002991}.

\bibitem[{\textit{Jones et~al.}(2001--present)\textit{Jones, Oliphant, Peterson
  et~al.}}]{jones2001}
Jones, E., T.~Oliphant, P.~Peterson, et~al. (2001--present), {SciPy}: Open
  source scientific tools for {Python}, [Online; accessed 2016-06-24].

\bibitem[{\textit{Kara et~al.}(2014)\textit{Kara, Bal, Tur, and
  Ates}}]{kara-etal2014}
Kara, I., O.~T. Bal, H.~Tur, and A.~Ates (2014), A new efficient method for
  topographic distortion correction, analytical continuation, vertical
  derivatives and using equivalent source technique: Application to field data,
  \textit{Journal of Applied Geophysics}, \textit{106}, 67--76,
  \doi{10.1016/j.jappgeo.2014.04.011}.

\bibitem[{\textit{Kirschvink et~al.}(2008)\textit{Kirschvink, Kopp, Raub,
  Baumgartner, and Holt}}]{kirschvink2008}
Kirschvink, J.~L., R.~E. Kopp, T.~D. Raub, C.~T. Baumgartner, and J.~W. Holt
  (2008), Rapid, precise, and high-sensitivity acquisition of paleomagnetic and
  rock-magnetic data: Development of a low-noise automatic sample changing
  system for superconducting rock magnetometers, \textit{Geochemistry,
  Geophysics, Geosystems}, \textit{9}(5), \doi{10.1029/2007GC001856}.

\bibitem[{\textit{Kirschvink et~al.}(2015)\textit{Kirschvink, Isozaki, Shibuya,
  ichiro Otofuji, Raub, Hilburn, Kasuya, Yokoyama, and
  Bonifacie}}]{kirschvink2015}
Kirschvink, J.~L., Y.~Isozaki, H.~Shibuya, Y.~ichiro Otofuji, T.~D. Raub, I.~A.
  Hilburn, T.~Kasuya, M.~Yokoyama, and M.~Bonifacie (2015), Challenging the
  sensitivity limits of paleomagnetism: Magnetostratigraphy of weakly
  magnetized guadalupian–lopingian (permian) limestone from kyushu, japan,
  \textit{Palaeogeography, Palaeoclimatology, Palaeoecology}, \textit{418}, 75
  -- 89, \doi{10.1016/j.palaeo.2014.10.037}.

\bibitem[{\textit{Lascu et~al.}(2012)\textit{Lascu, Jackson, and
  S{\o}lheid}}]{lascu2012}
Lascu, I., M.~Jackson, and P.~S{\o}lheid (2012), Beyond u-channels: improving
  the deconvolution of u-channel magnetometer data for non-standard sample
  geometries, \textit{IRM Quarterly}, \textit{22}(3).

\bibitem[{\textit{Le\~{a}o and Silva}(1989)}]{leao-silva1989}
Le\~{a}o, J. W.~D., and J.~B.~C. Silva (1989), Discrete linear transformations
  of potential field data, \textit{GEOPHYSICS}, \textit{54}(4), 497--507,
  \doi{10.1190/1.1442676}.

\bibitem[{\textit{Lee et~al.}(2004)\textit{Lee, Matthews, and
  Wellstood}}]{lee2004}
Lee, S.-Y., J.~Matthews, and F.~C. Wellstood (2004), Position noise in scanning
  superconducting quantum interference device microscopy, \textit{Appl. Phys.
  Lett.}, \textit{84}(24), 5001--5003, \doi{10.1063/1.1763215}.

\bibitem[{\textit{Li and Oldenburg}(2010)}]{li-oldenburg2010}
Li, Y., and D.~W. Oldenburg (2010), Rapid construction of equivalent sources
  using wavelets, \textit{GEOPHYSICS}, \textit{75}(3), L51--L59,
  \doi{10.1190/1.3378764}.

\bibitem[{\textit{Li et~al.}(2014)\textit{Li, Nabighian, and
  Oldenburg}}]{li-nabighian-oldenburg2014}
Li, Y., M.~Nabighian, and D.~W. Oldenburg (2014), Using an equivalent source
  with positivity for low-latitude reduction to the pole without striation,
  \textit{GEOPHYSICS}, \textit{79}(6), J81--J90, \doi{10.1190/geo2014-0134.1}.

\bibitem[{\textit{Lima et~al.}(2013)\textit{Lima, Weiss, Baratchart, Hardin,
  and Saff}}]{lima2013}
Lima, E.~A., B.~P. Weiss, L.~Baratchart, D.~P. Hardin, and E.~B. Saff (2013),
  Fast inversion of magnetic field maps of unidirectional planar geological
  magnetization, \textit{J. Geophys. Res.: Solid Earth}, \textit{118}(6),
  2723--2752, \doi{10.1002/jgrb.50229}.

\bibitem[{\textit{Lima et~al.}(2014)\textit{Lima, Bruno, Carvalho, and
  Weiss}}]{lima2014}
Lima, E.~A., A.~C. Bruno, H.~R. Carvalho, and B.~P. Weiss (2014), Scanning
  magnetic tunnel junction microscope for high-resolution imaging of remanent
  magnetization fields, \textit{Measurement Science and Technology},
  \textit{25}(10), 105,401, \doi{10.1088/0957-0233/25/10/105401}.

\bibitem[{\textit{Mareschal}(1985)}]{mareschal1985}
Mareschal, J.~C. (1985), Inversion of potential field data in fourier transform
  domain, \textit{Geophysics}, \textit{50}(4), 685--691,
  \doi{10.1190/1.1441943}.

\bibitem[{\textit{Mendon\c{c}a}(1992)}]{mendonca1992}
Mendon\c{c}a, C.~A. (1992), Interpola\c{c}\~{a}o de dados de campo potencial
  atrav\'{e}s da camada equivalente, Ph.D. thesis, Universidade Federal do
  Par\'{a}, Bel\'{e}m do Par\'{a}, Brazil.

\bibitem[{\textit{Mendon\c{c}a and Silva}(1994)}]{mendonca-silva1994}
Mendon\c{c}a, C.~A., and J.~B.~C. Silva (1994), The equivalent data concept
  applied to the interpolation of potential field data, \textit{GEOPHYSICS},
  \textit{59}(5), 722--732, \doi{10.1190/1.1443630}.

\bibitem[{\textit{Mendon\c{c}a and Silva}(1995)}]{mendonca-silva1995}
Mendon\c{c}a, C.~A., and J.~B.~C. Silva (1995), Interpolation of
  potential‐field data by equivalent layer and minimum curvature: A
  comparative analysis, \textit{GEOPHYSICS}, \textit{60}(2), 399--407,
  \doi{10.1190/1.1443776}.

\bibitem[{\textit{Nagata}(1961)}]{nagata1961}
Nagata, T. (1961), \textit{Rock magnetism}, second edition ed., Maruzen.

\bibitem[{\textit{Nagy et~al.}(2000)\textit{Nagy, Papp, and
  Benedek}}]{nagy2000}
Nagy, D., G.~Papp, and J.~Benedek (2000), The gravitational potential and its
  derivatives for the prism, \textit{Journal of Geodesy}, \textit{74}(7-8),
  311--326, \doi{10.1007/s001900000116}.

\bibitem[{\textit{Oda and Xuan}(2014)}]{oda-xuan2014}
Oda, H., and C.~Xuan (2014), Deconvolution of continuous paleomagnetic data
  from pass-through magnetometer: A new algorithm to restore geomagnetic and
  environmental information based on realistic optimization,
  \textit{Geochemistry, Geophysics, Geosystems}, \textit{15}(10), 3907--3924,
  \doi{10.1002/2014GC005513}.

>>>>

We have applied our method to invert the synthetic data produced
by a simulated rock sample (not shown) with $L_{x} = 16$~mm and 
$L_{y} = L_{z} = 3$~mm, according to the Figure \ref{fig:sample}.
This synthetic sample is formed by $P = 16$ juxtaposed prisms along 
the $x$-axis, where each prism has a uniform and high magnetization
(red dots in Figures \ref{fig:estimate-validation},
\ref{fig:estimate-pre-processing} and \ref{fig:estimate-sensor2sample}).
In all tests presented in this section, 
the simulated magnetic sensor has an square active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}). The
magnetic data produced by the synthetic sample on 
each plane $\alpha = 0, 1, 2, 3$ were calculated at
$N = 4,284$ points, on a set of $42$ regularly spaced lines 
that are parallel to the $x$-axis, each one with $102$ regularly
spaced points. The data were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $30$~$\mu$T. These data simulate
an observed data set.
Besides, we have simulated the misalignment problems 
described in the subsection \ref{subsec:Pre-processing}.
Table \ref{tab:misalignment-parameters} shows the parameters
$\theta$, $\Delta x^{\prime}$ and $\Delta y^{\prime}$ (Figure 
\ref{fig:acquisition_errors}b) representing these misalignments
in the magnetic data produced by the synthetic sample on
the planes $\alpha = 0, 1, 2, 3$.

@@

\bibliography{bib-file}
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

%\begin{thebibliography}{56}
%\providecommand{\natexlab}[1]{#1}
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%
%\bibitem[{\textit{Aster et~al.}(2005)\textit{Aster, Borchers, and
%  Thurber}}]{aster2005}
%Aster, R.~C., B.~Borchers, and C.~H. Thurber (2005), \textit{Parameter
%  Estimation and Inverse Problems, Volume 90 (International Geophysics)},
%  Academic Press.
%
%\bibitem[{\textit{Baratchart et~al.}(2013)\textit{Baratchart, Hardin, Lima,
%  Saff, and Weiss}}]{baratchart2013}
%Baratchart, L., D.~P. Hardin, E.~A. Lima, E.~B. Saff, and B.~P. Weiss (2013),
%  Characterizing kernels of operators related to thin-plate magnetizations via
%  generalizations of hodge decompositions, \textit{Inverse Problems},
%  \textit{29}(1), 015,004, \doi{10.1088/0266-5611/29/1/015004}.
%
%\bibitem[{\textit{Barnes}(2014)}]{barnes2014}
%Barnes, G. (2014), Reconstructing the gravity gradient anomaly field from
%  surveys with wide line spacing using equivalent source processing: an error
%  analysis, \textit{Geophysical Prospecting}, \textit{62}(3), 646--657,
%  \doi{10.1111/1365-2478.12098}.
%
%\bibitem[{\textit{Barnes and Lumley}(2011)}]{barnes-lumley2011}
%Barnes, G., and J.~Lumley (2011), Processing gravity gradient data,
%  \textit{GEOPHYSICS}, \textit{76}(2), I33--I47, \doi{10.1190/1.3548548}.
%
%\bibitem[{\textit{Baudenbacher et~al.}(2003)\textit{Baudenbacher, Fong, Holzer,
%  and Radparvar}}]{baudenbacher2003}
%Baudenbacher, F., L.~E. Fong, J.~R. Holzer, and M.~Radparvar (2003), Monolithic
%  low-transition-temperature superconducting magnetometers for high resolution
%  imaging magnetic fields of room temperature samples, \textit{Appl. Phys.
%  Lett.}, \textit{82}(20), 3487--3489,
%  \doi{http://dx.doi.org/10.1063/1.1572968}.
%
%\bibitem[{\textit{Blackett}(1952)}]{blackett1952}
%Blackett, P. M.~S. (1952), A negative experiment relating to magnetism and the
%  earth{\textquoteright}s rotation, \textit{Philosophical Transactions of the
%  Royal Society of London A: Mathematical, Physical and Engineering Sciences},
%  \textit{245}(897), 309--370, \doi{10.1098/rsta.1952.0024}.
%
%\bibitem[{\textit{Cordell}(1992)}]{cordell1992}
%Cordell, L. (1992), A scattered equivalent-source method for interpolation and
%  gridding of potential‐field data in three dimensions, \textit{GEOPHYSICS},
%  \textit{57}(4), 629--636, \doi{10.1190/1.1443275}.
%
%\bibitem[{\textit{Dampney}(1969)}]{dampney1969}
%Dampney, C. N.~G. (1969), The equivalent source technique, \textit{GEOPHYSICS},
%  \textit{34}(1), 39--53, \doi{10.1190/1.1439996}.
%
%\bibitem[{\textit{Dodson et~al.}(1974)\textit{Dodson, Fuller, and
%  Pilant}}]{dodson1974}
%Dodson, R., M.~Fuller, and W.~Pilant (1974), On the measurement of the remanent
%  magnetism of long cores, \textit{Geophysical Research Letters},
%  \textit{1}(4), 185--188, \doi{10.1029/GL001i004p00185}.
%
%\bibitem[{\textit{Egli and Heller}(2000)}]{egli2000}
%Egli, R., and F.~Heller (2000), High-resolution imaging using a high-tc
%  superconducting quantum interference device (squid) magnetometer, \textit{J.
%  Geophys. Res.: Solid Earth}, \textit{105}(B11), 25,709--25,727,
%  \doi{10.1029/2000JB900192}.
%
%\bibitem[{\textit{Emilia}(1973)}]{emilia1973}
%Emilia, D.~A. (1973), Equivalent sources used as an analytic base for
%  processing total magnetic field profiles, \textit{GEOPHYSICS},
%  \textit{38}(2), 339--348, \doi{10.1190/1.1440344}.
%
%\bibitem[{\textit{Engl et~al.}(1996)\textit{Engl, Hanke, and
%  Neubauer}}]{engl1996}
%Engl, H.~W., M.~Hanke, and A.~Neubauer (1996), \textit{Regularization of
%  Inverse Problems (Mathematics and Its Applications)}, Springer.
%
%\bibitem[{\textit{Fong et~al.}(2005)\textit{Fong, Holzer, McBride, Lima,
%  Baudenbacher, and Radparvar}}]{fong2005}
%Fong, L.~E., J.~R. Holzer, K.~K. McBride, E.~A. Lima, F.~Baudenbacher, and
%  M.~Radparvar (2005), High-resolution room-temperature sample scanning
%  superconducting quantum interference device microscope configurable for
%  geological and biomagnetic applications, \textit{Rev. Sci. Instrum.},
%  \textit{76}(5), \doi{10.1063/1.1884025}.
%
%\bibitem[{\textit{Fu et~al.}(2014)\textit{Fu, Lima, and Weiss}}]{fu2014}
%Fu, R., E.~Lima, and B.~Weiss (2014), No nebular magnetization in the allende
%  \{CV\} carbonaceous chondrite, \textit{Earth Planet. Sci. Lett.},
%  \textit{404}, 54--66, \doi{10.1016/j.epsl.2014.07.014}.
%
%\bibitem[{\textit{Gattacceca et~al.}(2006)\textit{Gattacceca, Boustie, Weiss,
%  Rochette, Lima, Fong, and Baudenbacher}}]{gattacceca2006}
%Gattacceca, J., M.~Boustie, B.~P. Weiss, P.~Rochette, E.~A. Lima, L.~E. Fong,
%  and F.~J. Baudenbacher (2006), Investigating impact demagnetization through
%  laser impacts and squid microscopy, \textit{Geology}, \textit{34}(5),
%  333--336, \doi{10.1130/G21898.1}.
%
%\bibitem[{\textit{Goree and Fuller}(1976)}]{goree-fuller1976}
%Goree, W.~S., and M.~Fuller (1976), Magnetometers using rf-driven squids and
%  their applications in rock magnetism and paleomagnetism, \textit{Reviews of
%  Geophysics}, \textit{14}(4), 591--608, \doi{10.1029/RG014i004p00591}.
%
%\bibitem[{\textit{Gusp\'{i} and Novara}(2009)}]{guspi-novara2009}
%Gusp\'{i}, F., and I.~Novara (2009), Reduction to the pole and transformations
%  of scattered magnetic data using newtonian equivalent sources,
%  \textit{GEOPHYSICS}, \textit{74}(5), L67--L73, \doi{10.1190/1.3170690}.
%
%\bibitem[{\textit{Hankard et~al.}(2009)\textit{Hankard, Gattacceca, Fermon,
%  Pannetier-Lecoeur, Langlais, Quesnel, Rochette, and McEnroe}}]{hankard2009}
%Hankard, F., J.~Gattacceca, C.~Fermon, M.~Pannetier-Lecoeur, B.~Langlais,
%  Y.~Quesnel, P.~Rochette, and S.~A. McEnroe (2009), Magnetic field microscopy
%  of rock samples using a giant magnetoresistance–based scanning
%  magnetometer, \textit{Geochem., Geophys., Geosyst.}, \textit{10}(10),
%  \doi{10.1029/2009GC002750}.
%
%\bibitem[{\textit{Hansen and Miyazaki}(1984)}]{hansen-miyazaki1984}
%Hansen, R.~O., and Y.~Miyazaki (1984), Continuation of potential fields between
%  arbitrary surfaces, \textit{GEOPHYSICS}, \textit{49}(6), 787--795,
%  \doi{10.1190/1.1441707}.
%
%\bibitem[{\textit{Hunter}(2007)}]{hunter2007}
%Hunter, J.~D. (2007), Matplotlib: A 2d graphics environment, \textit{Computing
%  in Science \& Engineering}, \textit{9}(3), 90--95,
%  \doi{10.1109/MCSE.2007.55}.
%
%\bibitem[{\textit{Jackson et~al.}(2010)\textit{Jackson, Bowles, Lascu, and
%  Solheid}}]{jackson2010}
%Jackson, M., J.~A. Bowles, I.~Lascu, and P.~Solheid (2010), Deconvolution of u
%  channel magnetometer data: Experimental study of accuracy, resolution, and
%  stability of different inversion methods, \textit{Geochemistry, Geophysics,
%  Geosystems}, \textit{11}(7), \doi{10.1029/2009GC002991}.
%
%\bibitem[{\textit{Jones et~al.}(2001--present)\textit{Jones, Oliphant, Peterson
%  et~al.}}]{jones2001}
%Jones, E., T.~Oliphant, P.~Peterson, et~al. (2001--present), {SciPy}: Open
%  source scientific tools for {Python}, [Online; accessed 2016-06-24].
%
%\bibitem[{\textit{Kara et~al.}(2014)\textit{Kara, Bal, Tur, and
%  Ates}}]{kara-etal2014}
%Kara, I., O.~T. Bal, H.~Tur, and A.~Ates (2014), A new efficient method for
%  topographic distortion correction, analytical continuation, vertical
%  derivatives and using equivalent source technique: Application to field data,
%  \textit{Journal of Applied Geophysics}, \textit{106}, 67--76,
%  \doi{10.1016/j.jappgeo.2014.04.011}.
%
%\bibitem[{\textit{Kirschvink et~al.}(2008)\textit{Kirschvink, Kopp, Raub,
%  Baumgartner, and Holt}}]{kirschvink2008}
%Kirschvink, J.~L., R.~E. Kopp, T.~D. Raub, C.~T. Baumgartner, and J.~W. Holt
%  (2008), Rapid, precise, and high-sensitivity acquisition of paleomagnetic and
%  rock-magnetic data: Development of a low-noise automatic sample changing
%  system for superconducting rock magnetometers, \textit{Geochemistry,
%  Geophysics, Geosystems}, \textit{9}(5), \doi{10.1029/2007GC001856}.
%
%\bibitem[{\textit{Kirschvink et~al.}(2015)\textit{Kirschvink, Isozaki, Shibuya,
%  ichiro Otofuji, Raub, Hilburn, Kasuya, Yokoyama, and
%  Bonifacie}}]{kirschvink2015}
%Kirschvink, J.~L., Y.~Isozaki, H.~Shibuya, Y.~ichiro Otofuji, T.~D. Raub, I.~A.
%  Hilburn, T.~Kasuya, M.~Yokoyama, and M.~Bonifacie (2015), Challenging the
%  sensitivity limits of paleomagnetism: Magnetostratigraphy of weakly
%  magnetized guadalupian–lopingian (permian) limestone from kyushu, japan,
%  \textit{Palaeogeography, Palaeoclimatology, Palaeoecology}, \textit{418}, 75
%  -- 89, \doi{10.1016/j.palaeo.2014.10.037}.
%
%\bibitem[{\textit{Lascu et~al.}(2012)\textit{Lascu, Jackson, and
%  S{\o}lheid}}]{lascu2012}
%Lascu, I., M.~Jackson, and P.~S{\o}lheid (2012), Beyond u-channels: improving
%  the deconvolution of u-channel magnetometer data for non-standard sample
%  geometries, \textit{IRM Quarterly}, \textit{22}(3).
%
%\bibitem[{\textit{Le\~{a}o and Silva}(1989)}]{leao-silva1989}
%Le\~{a}o, J. W.~D., and J.~B.~C. Silva (1989), Discrete linear transformations
%  of potential field data, \textit{GEOPHYSICS}, \textit{54}(4), 497--507,
%  \doi{10.1190/1.1442676}.
%
%\bibitem[{\textit{Lee et~al.}(2004)\textit{Lee, Matthews, and
%  Wellstood}}]{lee2004}
%Lee, S.-Y., J.~Matthews, and F.~C. Wellstood (2004), Position noise in scanning
%  superconducting quantum interference device microscopy, \textit{Appl. Phys.
%  Lett.}, \textit{84}(24), 5001--5003, \doi{10.1063/1.1763215}.
%
%\bibitem[{\textit{Li and Oldenburg}(2010)}]{li-oldenburg2010}
%Li, Y., and D.~W. Oldenburg (2010), Rapid construction of equivalent sources
%  using wavelets, \textit{GEOPHYSICS}, \textit{75}(3), L51--L59,
%  \doi{10.1190/1.3378764}.
%
%\bibitem[{\textit{Li et~al.}(2014)\textit{Li, Nabighian, and
%  Oldenburg}}]{li-nabighian-oldenburg2014}
%Li, Y., M.~Nabighian, and D.~W. Oldenburg (2014), Using an equivalent source
%  with positivity for low-latitude reduction to the pole without striation,
%  \textit{GEOPHYSICS}, \textit{79}(6), J81--J90, \doi{10.1190/geo2014-0134.1}.
%
%\bibitem[{\textit{Lima et~al.}(2013)\textit{Lima, Weiss, Baratchart, Hardin,
%  and Saff}}]{lima2013}
%Lima, E.~A., B.~P. Weiss, L.~Baratchart, D.~P. Hardin, and E.~B. Saff (2013),
%  Fast inversion of magnetic field maps of unidirectional planar geological
%  magnetization, \textit{J. Geophys. Res.: Solid Earth}, \textit{118}(6),
%  2723--2752, \doi{10.1002/jgrb.50229}.
%
%\bibitem[{\textit{Lima et~al.}(2014)\textit{Lima, Bruno, Carvalho, and
%  Weiss}}]{lima2014}
%Lima, E.~A., A.~C. Bruno, H.~R. Carvalho, and B.~P. Weiss (2014), Scanning
%  magnetic tunnel junction microscope for high-resolution imaging of remanent
%  magnetization fields, \textit{Measurement Science and Technology},
%  \textit{25}(10), 105,401, \doi{10.1088/0957-0233/25/10/105401}.
%
%\bibitem[{\textit{Mareschal}(1985)}]{mareschal1985}
%Mareschal, J.~C. (1985), Inversion of potential field data in fourier transform
%  domain, \textit{Geophysics}, \textit{50}(4), 685--691,
%  \doi{10.1190/1.1441943}.
%
%\bibitem[{\textit{Mendon\c{c}a}(1992)}]{mendonca1992}
%Mendon\c{c}a, C.~A. (1992), Interpola\c{c}\~{a}o de dados de campo potencial
%  atrav\'{e}s da camada equivalente, Ph.D. thesis, Universidade Federal do
%  Par\'{a}, Bel\'{e}m do Par\'{a}, Brazil.
%
%\bibitem[{\textit{Mendon\c{c}a and Silva}(1994)}]{mendonca-silva1994}
%Mendon\c{c}a, C.~A., and J.~B.~C. Silva (1994), The equivalent data concept
%  applied to the interpolation of potential field data, \textit{GEOPHYSICS},
%  \textit{59}(5), 722--732, \doi{10.1190/1.1443630}.
%
%\bibitem[{\textit{Mendon\c{c}a and Silva}(1995)}]{mendonca-silva1995}
%Mendon\c{c}a, C.~A., and J.~B.~C. Silva (1995), Interpolation of
%  potential‐field data by equivalent layer and minimum curvature: A
%  comparative analysis, \textit{GEOPHYSICS}, \textit{60}(2), 399--407,
%  \doi{10.1190/1.1443776}.
%
%\bibitem[{\textit{Nagata}(1961)}]{nagata1961}
%Nagata, T. (1961), \textit{Rock magnetism}, second edition ed., Maruzen.
%
%\bibitem[{\textit{Nagy et~al.}(2000)\textit{Nagy, Papp, and
%  Benedek}}]{nagy2000}
%Nagy, D., G.~Papp, and J.~Benedek (2000), The gravitational potential and its
%  derivatives for the prism, \textit{Journal of Geodesy}, \textit{74}(7-8),
%  311--326, \doi{10.1007/s001900000116}.
%
%\bibitem[{\textit{Oda and Xuan}(2014)}]{oda-xuan2014}
%Oda, H., and C.~Xuan (2014), Deconvolution of continuous paleomagnetic data
%  from pass-through magnetometer: A new algorithm to restore geomagnetic and
%  environmental information based on realistic optimization,
%  \textit{Geochemistry, Geophysics, Geosystems}, \textit{15}(10), 3907--3924,
%  \doi{10.1002/2014GC005513}.
%
%\bibitem[{\textit{Oda et~al.}(2011)\textit{Oda, Usui, Miyagi, Joshima, Weiss,
%  Shantz, Fong, McBride, Harder, and Baudenbacher}}]{oda2011}
